\documentclass{article}
    \usepackage[margin=0.7in]{geometry}
    \usepackage[parfill]{parskip}
    \usepackage[utf8]{inputenc}
    \usepackage{hyperref}
    
    % Related to math
    \usepackage{amsmath,amssymb,amsfonts,amsthm}

\begin{document}

% NOTE: See 
% - centering: https://tex.stackexchange.com/questions/23650/when-should-we-use-begincenter-instead-of-centering
% - subheadings: https://tex.stackexchange.com/questions/417429/how-to-make-subheadings
\newcommand{\chapsubhead}[1]{{ \begin{center}\Large #1 \vspace{2ex} \end{center} }}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\phantomsection\label{adrian-cederberg}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
    \section*{Adrian Cederberg}
\end{center}

\chapsubhead{
    adrn.cederberg123@gmail.com
    \textbar{} \href{https://github.com/acederberg}{Github} \textbar{}
    \href{https://acederberg.io}{acederberg.io}
}

\begin{center}
\section*{Education}\label{education}
\end{center}
\textbf{University of New Mexico, Spring 2015 - Fall 2019}
\begin{itemize}
\tightlist
\item[--]
  Bachelors of Science in applied mathematics (GPA 3.3) - Minor in chemistry.
\item[--]
  Worked as a grader, tutor, and researcher. Got my first tastes of software development with \texttt{matlab} and \texttt{python}.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
    \section*{Relevant Work}\label{relevant-work}
\end{center}

Read more about my recent projects \href{https://acederberg.io/home}{on my portfolio} or \href{https://github.com/acederberg}{on github}. This document is meant to be a synopsis and everything will not fit - and either of these resources will tell you more about my capabilities than this document ever could.

% --------------------------------------------------------------------------- %
\subsection*{\texorpdfstring{Founder \textbar{}  \texttt{Captura} and
\texttt{acederberg.io}}{Founder | Captura and acederberg.io}}\label{founder-of-captura-and-acederberg.io}

\textbf{January 2024 - Now}

My personal projects which I intend to use to grow a business and apply for a new job. 


\begin{itemize}
\tightlist
\item[--]
  Designed, implemented, tested, and deployed \texttt{Captura} using \texttt{fastapi}, \texttt{sqlalchemy}, \texttt{pydantic}, and \texttt{docker}. To learn
  more about \texttt{Captura} and get a demo, check out the
  \href{https://captura.acederbebrg.io}{Captura demo} or run the \texttt{docker-compose} project in the \href{https://github.com/acederberg/captura}{github repository}. Designed the \href{https://github.com/acederberg/captura-text}{captura-text} plugin to serve web assets that may be collaborated upon.
\item[--]
  Implemented infrastructure as code and continuous integration and deployment for \texttt{Captura} to \texttt{linode} using \texttt{pulumi} and \texttt{python}. Implemented \texttt{SSL} termination using \texttt{traefik}, \texttt{let's encrypt} ACME certificates, and \texttt{porkbun API} automation. Code is host on \texttt{github} but is only available upon request since I'd rather have deployment be opaque for the time being.
\item[--]
  Built \href{https://acederberg.io/home}{acederberg.io} using the \href{https://github.com/acederberg/captura-text}{captura-text} plugin and added some simple projects for visitors to enjoy in the browser.
\item[--]
  Maintained and published \href{https://github.com/acederberg/yaml-settings-pydantic}{a little \texttt{yaml configuration} library}. Added features, addressed issues, and tested.

\end{itemize}

% --------------------------------------------------------------------------- %
\subsection*{Software Engineer and Senior Software Engineer \textbar{}
Mountain Vector
Energy}\label{software-engineer-and-senior-software-engineer-mountain-vector-energy}

\textbf{January 2022 - December 2023}

\begin{itemize}
\tightlist
\item[--]
  Collaborated with 3 to 4 other developers to design, implement, maintain,
  and deploy \texttt{Cufflink} Software as a Service from almost nothing. Assisted those struggling with their work (when they existed), contributed to \texttt{Cufflink} client and admin dashboards within the \texttt{react} and \texttt{next} frameworks, and wrote the \texttt{Cufflink API}.
\item[--]
  Bootstrapped the \texttt{Cufflink API} from former CTOs notes/prototype when
  he unexpectedly quit (right when I started). Used \texttt{FastAPI}, \texttt{SQLAlchemy}, and \texttt{Pydantic}. Wrote data pipelines, managed databases, resolved bugs, and added features. Implemented \texttt{Auth0} authentication.
\item[--]
  Developed infrastructure as code using \texttt{terraform} on \texttt{azure} and designed \texttt{helm} charts for \texttt{Cufflink} services. Managed and debugged services in \texttt{kubernetes}. Built \texttt{bitbucket} pipelines for various repositories and implemented/maintained
  continuous integration and deployment. Maintained service up-time and reliability.
\item[--]
  Used \texttt{atlassian jira} to track progress, keep notes, and assign issues.
\item[--]
  Performed technical interviews to hire two software engineers.
\end{itemize}

% --------------------------------------------------------------------------- %
\subsection*{Developer and Devops Engineer \textbar{} My Portfolio and
Self-Study}\label{developer-and-devops-engineer-my-portfolio-and-self-study}

\begin{itemize}
\tightlist
\item[--]
  Studied software 50+ hours a week because I wanted a job in the subject matter. Starting January 2021 and continuing until January
  2022.
\item[--]
  Built a portfolio using \texttt{flask} and deployed it with
  \texttt{ansible} and \texttt{docker-compose}. Code is available upon request.
\end{itemize}

% --------------------------------------------------------------------------- %
\subsection*{Research Assistant \textbar{} University of New Mexico
Department of Mechanical
Engineering}\label{research-assistant-university-of-new-mexico-department-of-mechanical-engineering}

\textbf{Summer 2019 - Winter 2020}

\begin{itemize}
\tightlist
\item[--]
  Collaborated with Craig Davidson of Dark Sea Industries to develop and
  document relatively efficient air plasma production using
  magnetohydrodynamic methods.
\item[--]
  Built and programmed sensor arrays using Raspberry and Arduino and
  wrote drivers in \texttt{python} and \texttt{c}.
\item[--]
  Processed experimental data using python to generate graphs.
  Interpreted spectrometer data using Python to increase productivity.
  Built various components for experimental setup including a power
  supply array.
\end{itemize}

% --------------------------------------------------------------------------- %
\subsection*{Grader \textbar{} University of New Mexico Department of
Mathematics}\label{grader-university-of-new-mexico-department-of-mathematics}

\textbf{Fall 2019 and Fall 2020}

\begin{itemize}
\tightlist
\item[--]
  Provided useful feedback and grading on undergraduate homework on a
  routine basis. Courses include partial differential equations, linear
  algebra, and college algebra. Worked in coordination with professors.
\end{itemize}

% --------------------------------------------------------------------------- %
\subsection*{Tutor \textbar{} University of New Mexico Math and Learning
Lab}\label{tutor-university-of-new-mexico-math-and-learning-lab}

\textbf{Fall 2017 - Summer 2019}

\begin{itemize}
\tightlist
\item[--]
  Improved student outcomes in basic algebra classes using the ALEKs
  program by providing students individual attention.
\end{itemize}

% --------------------------------------------------------------------------- %
\begin{center}
\section*{Skills and Tools}\label{skills-and-tools}
\end{center}

\begin{itemize}
\tightlist
\item[--]
  Languages: \texttt{Python}, \texttt{Javascript}, \texttt{HCL},
  \texttt{Go}.
\item[--]
  Tools: \texttt{Kubernetes}, \texttt{Docker}, \texttt{Helm},
  \texttt{Traefik}, \texttt{Terraform}, \texttt{Pulumi}.
\item[--]
  Libraries: \texttt{Pydantic}, \texttt{FastAPI}, \texttt{Typer},
  \texttt{SQLAlchemy}, \texttt{NextJS}, Etc.
\item[--]
  Data: \texttt{YAML}, \texttt{JSON}, \texttt{CSS}, \texttt{HTML},
  \texttt{XML}, \texttt{TOML}.
\item[--]
  Etc: \texttt{Pipelines}, \texttt{Infrastructure\ as\ Code},
  \texttt{Continuous\ Integration\ and\ Deployment}.
\item[--]
  Databases: \texttt{MySQL}, \texttt{MongoDB}, \texttt{Redis}.
\item[--]
  Operating Systems: \texttt{Linux}, \texttt{Windows}.
\item[--]
  Editing tools: \texttt{Vim}, \texttt{Neovim},
  \texttt{Visual\ Studio\ Code}.
\end{itemize}
\end{document}



